---
title: "metacheck"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{metacheck}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>"
)
```


## Installation

You can install the development version of metacheck from [GitHub](https://github.com/scienceverse/metacheck) with:

``` r
# install.packages("devtools")
devtools::install_github("scienceverse/metacheck")
```

```{r}
#| eval: false
library(metacheck)
```

```{r}
#| include: false
devtools::load_all(".")
```


You can launch an interactive shiny app version of the code below with:

``` r
metacheck_app()
```

### Load from PDF

The function `convert()` can read PDF files and save them in [JSON format](https://www.scienceverse.org/schema/paper.json). This requires an internet connection and takes a few seconds per paper, so should only be done once and the results saved for later use.

```{r, eval = FALSE}
pdf_file <- demofile("pdf")
json_file <- convert(file_path = pdf_file, save_path = "converted")
```

```{r, include = FALSE}
# doesn't require a call to the grobid server
json_file <- demofile("json")
```

You can set up your own local grobid server following instructions from <https://grobid.readthedocs.io/>. The easiest way is to use Docker.

``` bash
docker run --rm --init --ulimit core=0 -p 8070:8070 lfoppiano/grobid:0.9.0
```

Then you can set your api_url to the local path <http://localhost:8070>.

```{r, eval = FALSE}
json_file <- convert(file_path = pdf_file, 
                     save_path = "converted",
                     method = "grobid",
                     api_url = "http://localhost:8070")
```


### Load from JSON

The function `read()` can read converted JSON files.

```{r}
paper <- read(json_file)
```

### Load from non-PDF document

To take advantage of grobid's ability to parse references and other aspects of papers, for now the best way is to convert your papers to PDF. We will introduce our custom backend, bibr, soon and this will be able to convert DOC and DOCX files directly.

### Batch Processing

The functions `convert()` and `read()` also work on a folder of files, returning a list of JSON file paths or paper objects, respectively. The functions `search_text()`, `expand_text()` and `llm()` also work on a list of paper objects.

## Paper Components

Paper objects contain a lot of structured information, including info, references, and citations.

### Info

```{r}
paper$info
```

### Bibliography

The bibliography is provided in a tabular format.

```{r, eval = FALSE}
paper$bib
```

```{r, echo = FALSE}
knitr::kable(paper$bib)
```

### Cross-References

Cross-references are also provided in a tabular format, with `xref_id` to match the bibliography table.

```{r, eval = FALSE}
paper$xref
```

```{r, echo = FALSE}
knitr::kable(paper$xref)
```

### Batch

There are functions to combine the infomation from a list of papers, like the `psychsci` built-in dataset of 250 open access papers from Psychological Science.

```{r}
paper_table(psychsci[1:5], "info", c("title", "doi"))
```


```{r}
paper_table(psychsci[1:5], "bib") |>
  dplyr::filter(!is.na(doi))
```

## Search Text

You can access a parsed table of the full text of the paper via `paper$text`, but you may find it more convenient to use the function `search_text()`. The defaults return a data table of each sentence, with the section type, header, div, paragraph and sentence numbers, and file name. (The section type is a best guess from the headers, so may not always be accurate.)

```{r}
text <- search_text(paper)
```

```{r, echo = FALSE}
head(text) |>
  knitr::kable()
```

### Pattern

You can search for a specific word or phrase by setting the `pattern` argument. The pattern is a regex string by default; set `fixed = TRUE` if you want to find exact text matches.

```{r}
text <- search_text(paper, pattern = "metacheck")
```

```{r, echo = FALSE}
knitr::kable(text)
```

### Return

Set `return` to one of "sentence", "paragraph", "section", or "match" to control what gets returned.

```{r}
text <- search_text(paper, "GitHub", 
                    return = "paragraph")
```

```{r, echo = FALSE}
knitr::kable(text)
```


### Regex matches

You can also return just the matched text from a regex search by setting `return = "match"`. The extra `...` arguments in `search_text()` are passed to `grep()`, so `perl = TRUE` allows you to use more complex regex, like below.

```{r}
pattern <- "[a-zA-Z]\\S*\\s*(=|<)\\s*[0-9\\.,-]*\\d"
text <- search_text(paper, pattern, return = "match", perl = TRUE)
```

```{r, echo = FALSE}
knitr::kable(text)
```

### Expand Text

You can expand the text returned by `search_text()` or a module with `expand_text()`.

```{r}
marginal <- search_text(paper, "marginal") |>
  expand_text(paper, plus = 1, minus = 1)

marginal[, c("text", "expanded")]
```



## Large Language Models

You can query the extracted text of papers with LLMs using any models supported by [ellmer](https://ellmer.tidyverse.org/).

### Setup

You will need to get **your own API key** (the one below is a fake example) from your preferred provider (e.g. <https://console.groq.com/keys>). To avoid having to type it out, add it to the .Renviron file in the following format (you can use `usethis::edit_r_environ()` to access the .Renviron file).

``` bash
GROQ_GPT_KEY="sk-proj-abcdefghijklmnopqrs0123456789ABCDEFGHIJKLMNOPQRS"
```

```{r, eval=FALSE}
# useful if you aren't sure where this file is
usethis::edit_r_environ()
```

You can get or set the default LLM model with `llm_model()` and access a list of the current available models using `llm_model_list()`. 

```{r, echo = FALSE}
modlist <- llm_model_list("groq")

knitr::kable(modlist[1:5,])
```

When you start metacheck for the first time, it will check for relevant API keys in your Renviron and automatically set the model to use. You can get or set this with `llm_model()`. 

```{r}
#| eval: false
llm_model() # get current model
llm_model("groq") # set to ellmer's default groq model
llm_model("groq/llama-3.3-70b-versatile") # set to specific openai model
```


### LLM Queries

You can query the extracted text of papers with LLMs. See `?llm` for details of how to get and set up your API key, choose an LLM, and adjust settings. 

Use `search_text()` first to narrow down the text into what you want to query. Below, we limited search to the first ten papers, and returned sentences that contains the word "power" and at least one number. Then we asked an LLM to determine if this is an a priori power analysis, and if so, to return some relevant values in a JSON-structured format.

```{r}
#| eval: false
power <- psychsci[1:10] |>
  # sentences containing the word power
  search_text("power") |>
  # and containing at least one number
  search_text("[0-9]") 

# ask a specific question with specific response format
system_prompt <- 'Does this sentence report an a priori power analysis? If so, return the test, sample size, critical alpha criterion, power level, effect size and effect size metric plus any other relevant parameters, in JSON format like:

{
  "apriori": true, 
  "test": "paired samples t-test", 
  "sample": 20, 
  "alpha": 0.05, 
  "power": 0.8, 
  "es": 0.4, 
  "es_metric": "cohen\'s D"
}

If not, return {"apriori": false}

Answer only in valid JSON format, starting with { and ending with }.'

llm_power <- llm(power, system_prompt)
```


```{r}
#| echo: false
# dput(llm_power)
llm_power <- structure(list(text_id = c(170L, 38L, 29L, 30L, 71L, 154L, 207L, 
40L, 84L, 88L, 89L, 148L, 209L), paragraph_id = c(41L, 11L, 11L, 
11L, 18L, 38L, 58L, 11L, 20L, 20L, 20L, 36L, 49L), section_id = c(9L, 
3L, 3L, 3L, 5L, 9L, 17L, 3L, 5L, 5L, 5L, 7L, 9L), text = c("It is possible that less-consistent effects were observed on trials with errors because of reduced power to detect an effect on these trials, which by design were less numerous (~25%).", 
"Figure 1 shows that CY had very little predictive power for CLIM, but the fit in the transposed plot has an obvious bell-shaped curve.", 
"Sample size was calculated with an a priori power analysis, using the effect sizes reported by Küpper et al. (2014), who used identical procedures, materials, and dependent measures.", 
"We determined that a minimum sample size of 7 per group would be necessary for 95% power to detect an effect.", 
"For the first part of the task, 11 static visual images, one from each of the scenes in the film were presented once each on a black background for 2 s using Power-Point.", 
"A sample size of 26 per group was required to ensure 80% power to detect this difference at the 5% significance level.", 
"A sample size of 18 per condition was required in order to ensure an 80% power to detect this difference at the 5% significance level.", 
"The 13,500 selected loan requests conservatively achieved a power of .98 for an effect size of .07 at an alpha level of .05.", 
"On the basis of simulations over a range of expected effect sizes for contrasts of fMRI activity, we estimated that a sample size of 24 would provide .80 power at a conservative brainwide alpha threshold of .002 (although such thresholds ideally should be relaxed for detecting activity in regions where an effect is predicted).", 
"Stimulus sample size was determined via power analysis of the sole existing similar study, which used neural activity to predict Internet downloads of music (Berns & Moore, 2012).", 
"The effect size from that study implied that a sample size of 72 loan requests would be required to achieve .80 power at an alpha level of .05.", 
"Categorical ratings of the emotional expressions in the loan photographs had a similarly powerful impact on loan-request success; requests with \"happy\" photographs received $5.15 more per hour than requests with \"sad\" photographs, on average; they achieved full funding in 7.6% less time.", 
"Although previous research has provided mixed evidence about the impact of positive versus negative affect on charitable giving (Andreoni, 1990;Small & Verrochi, 2009), by simultaneously assessing affect at both Internet-aggregate and laboratory-sample levels of analysis, our studies provide consistent evidence that photograph-elicited positive arousal most powerfully promoted lending rates and outcomes (Tables 1 and 2, Fig. 2a, and Fig."
), page_number = c(NA_integer_, NA_integer_, NA_integer_, NA_integer_, 
NA_integer_, NA_integer_, NA_integer_, NA_integer_, NA_integer_, 
NA_integer_, NA_integer_, NA_integer_, NA_integer_), paper_id = c("0956797614557697", 
"0956797614566469", "0956797615569889", "0956797615569889", "0956797615583071", 
"0956797615583071", "0956797615583071", "0956797615588467", "0956797615588467", 
"0956797615588467", "0956797615588467", "0956797615588467", "0956797615588467"
), header = c("General Discussion", "Analysis and Results", "Participants", 
"Participants", "Memory-reactivation task.", "Statistical analysis.", 
"Statistical analysis.", "Internet study", "Power analysis and sample size.", 
"Power analysis and sample size.", "Power analysis and sample size.", 
"Internet study", "Discussion"), section_type = c("discussion", 
"results", "method", "method", "method", "method", "method", 
"method", "method", "method", "method", "results", "discussion"
), answer = structure(c("{\"apriori\": false}", "{\"apriori\": false}", 
"{\n  \"apriori\": true\n}", "{\n  \"apriori\": true, \n  \"test\": \"t-test\", \n  \"sample\": 7, \n  \"alpha\": 0.05, \n  \"power\": 0.95\n}", 
"{\"apriori\": false}", "{\n  \"apriori\": true, \n  \"test\": \"two-sample t-test\", \n  \"sample\": 26, \n  \"alpha\": 0.05, \n  \"power\": 0.8\n}", 
"{\n  \"apriori\": true, \n  \"test\": \"t-test\", \n  \"sample\": 18, \n  \"alpha\": 0.05, \n  \"power\": 0.8\n}", 
"{\n  \"apriori\": true, \n  \"test\": null, \n  \"sample\": 13500, \n  \"alpha\": 0.05, \n  \"power\": 0.98, \n  \"es\": 0.07, \n  \"es_metric\": null\n}", 
"{\n  \"apriori\": true, \n  \"test\": \"fMRI activity contrast\", \n  \"sample\": 24, \n  \"alpha\": 0.002, \n  \"power\": 0.8\n}", 
"{\"apriori\": true}", "{\n  \"apriori\": true, \n  \"test\": null, \n  \"sample\": 72, \n  \"alpha\": 0.05, \n  \"power\": 0.8, \n  \"es\": null, \n  \"es_metric\": null\n}", 
"{\"apriori\": false}", "{\"apriori\": false}"), class = "ellmer_output")), row.names = c(NA, 
-13L), class = c("metacheck_llm", "data.frame"), llm = list(system_prompt = "Does this sentence report an a priori power analysis? If so, return the test, sample size, critical alpha criterion, power level, effect size and effect size metric plus any other relevant parameters, in JSON format like:\n{\n  \"apriori\": true, \n  \"test\": \"paired samples t-test\", \n  \"sample\": 20, \n  \"alpha\": 0.05, \n  \"power\": 0.8, \n  \"es\": 0.4, \n  \"es_metric\": \"cohen's D\"\n}\nIf not, return {\"apriori\": false}\nAnswer only in valid JSON format, starting with { and ending with }.", 
    model = "groq/llama-3.3-70b-versatile", type = NULL))

```

### Expand JSON

It is useful to ask an LLM to return data in JSON structured format, but can be frustrating to extract the data, especially where the LLM makes syntax mistakes. The function `json_expand()` tries to expand a column with a JSON-formatted response into columns and deals with it gracefully (sets an 'error' column to "parsing error") if there are errors. It also fixes column data types, if possible. 

```{r}
llm_response <- json_expand(llm_power, "answer") |>
  dplyr::select(text, apriori:es_metric)
```

```{r}
#| echo: false

knitr::kable(llm_response)
```

### Rate Limiting

The `llm()` function makes a separate query [^parallel] for each row in a data frame from `search_text()`. To prevent accidentally making way too many calls because of errors in your code, we set the default limits to 30 queries at a time, but you can change this:

```{r}
llm_max_calls(30)
```

[^parallel]: Using the parallel functions in ellmer can be more efficient, but currently doesn't do a good job of associating structured output to the input text when input may have 0+ outputs.

## OSF Functions

Metacheck provides several function to help you assess resources archived on the Open Science Framework.

### OSF Links and IDs

Get any OSF links from a paper or list of papers.

```{r}
links <- osf_links(psychsci)

links$text |> unique() |> head()
```

You can see that some of them have rogue spaces or view-only links. The function `osf_check_id()` takes most formats of OSF links (with or without https:// and osf.io/, as well as the 25-character waterbutler IDs) and converts them to short IDs. 

```{r}
osf_ids <- osf_check_id(links$text) |> unique()

head(osf_ids)
```

However, all of the `osf_***()` functions fix IDs for you and handle duplicate IDs without making extra API calls, so you don't need to add this step to most workflows.

### OSF Info

Get basic information about OSF links, such as the name, description, osf_type (nodes, files, preprints, registrations, users, set to "private" if you don't have authorisation to view it, and "invalid" if the ), whether it is public

```{r}
info <- osf_retrieve(links[1:6, "text"])

info[, c("text","osf_id", "osf_type", "public", "category")]
```

For now, the OSF API does not let us retrieve any information about view-only links. They may be viewable by you in the web browser if the link is still active, but will be listed in the table as public = FALSE and osf_type = "private". 

You can set the argument `recursive = TRUE` to also retrieve information about all nodes and files that are contained by the OSF link.

```{r}
osf_api_calls(0)
all_contents <- osf_retrieve(links$text[1], recursive = TRUE)
n_calls <- osf_api_calls()
```

The function `osf_api_calls()` lets you reset and retrieve the number of API calls made since the last reset. You can see that the project `r links$text[[1]]` had `r sum(all_contents$osf_type == "nodes")` nodes and `r sum(all_contents$osf_type == "files")` files, which required `r n_calls` API calls. 

```{r}
sum(all_contents$osf_type == "nodes")
```

### Download OSF Files

OSF projects let you organise information into nested components, and files within those components. Therefore, to retrieve all of the files associate with a project, you may need to navigate to several components and download zip files for the files from each components, then reorganise and rename the downloaded folders. 

The function `osf_file_download()` does all of this for you, recreating a folder structure based on the component names and downloading all files smaller than `max_file_size` (defaults to 10 MB) up to a total size of `max_download_size` (defaults to 100 MB).

```{r}
#| eval: false
osf_file_download(osf_id = "pngda",
                  download_to = ".", 
                  max_file_size = 1, 
                  max_download_size = 10)
```
```
Starting retrieval for pngda
- omitting metacheck.png (1.5MB)
Downloading files [=====================] 24/24 00:00:35
```

```{r}
#| eval: false
list.files("pngda", recursive = TRUE)
```

```{r}
#| echo: false

# list.files("articles/pngda/", recursive = TRUE) |> dput()
c(
  "Data/Individual/data-01.csv",
  "Data/Individual/data-02.csv",
  "Data/Individual/data-03.csv",
  "Data/Individual/data-04.csv",
  "Data/Individual/data-05.csv",
  "Data/Individual/data-06.csv",
  "Data/Individual/data-07.csv",
  "Data/Individual/data-08.csv",
  "Data/Individual/data-09.csv",
  "Data/Individual/data-10.csv",
  "Data/Individual/data-11.csv",
  "Data/Individual/data-12.csv",
  "Data/Individual/data-13.csv",
  "Data/Individual/data-14.csv",
  "Data/Processed Data/processed-data.csv",
  "Data/Raw Data/data.xlsx",
  "Data/Raw Data/nest-1/nest-2/nest-3/nest-4/test-4.txt",
  "Data/Raw Data/nest-1/nest-2/nest-3/test-3.txt",
  "Data/Raw Data/nest-1/nest-2/test-2.txt",
  "Data/Raw Data/nest-1/README",
  "Data/Raw Data/nest-1/test-1.txt",
  "Data/Raw Data/README",
  "README"
)
```



## Modules

metacheck is designed modularly, so you can add modules to check for anything. It comes with a set of pre-defined modules, and we hope people will share more modules.

### Module List

You can see the list of built-in modules with the function below.

```{r}
module_list()
```

### Running modules

To run a built-in module on a paper, you can reference it by name.

```{r}
p <- module_run(paper, "all_p_values")
```

```{r, echo = FALSE}
knitr::kable(p$table)
```

### Creating modules

You can create your own modules using R code. Modules can also contain instructions for reporting, to give "traffic lights" for whether a check passed or failed, and to include appropriate text feedback in a report. See the [modules vignette](modules.html) for more details. 


## Reports

You can generate a report from any set of modules. Check the function help for the default set.

```{r, eval = FALSE}
report(paper, output_format = "qmd")
```

See the [example report](../report-example.html).




