---
title: MetaCheck Report
subtitle: "%s"
metacheck:
  version: "%s"
  report-created: "%s"
format:
  html:
    theme: 
      light: flatly
      dark: darkly
    respect-user-color-scheme: true
    toc: true
    toc-title: >
      <ul class="emoji-key">
        <li class="red">⚠️ possible problems detected;</li> 
        <li class="yellow">🔍 something to check;</li> 
        <li class="green">✅️ no problems detected;</li>  
        <li class="info">ℹ️ informational only;</li>  
        <li class="na">⚪️ not applicable;</li>  
        <li class="fail">☠️ check failed</li>
      <ul>
      <hr/>
      **Table of Contents**
    toc-location: right
    toc-expand: 3
    page-layout: full
    title-block-banner: "#15342A"    #"#327118"
    title-block-banner-color: "white"
    link-external-newwindow: true
    embed-resources: true
    format-links: false
    smooth-scroll: true
execute: 
  echo: false
  error: true
---

<style>
  #TOC * { border-left: none; }
  #TOC > ul { border-left: 1px solid #15342A; }
  #TOC > ul > li > ul > li { text-indent: -1.2em; margin-left: 1.2em; }
  main h2, main h3 { margin-left: -20px; }
  main h2 { font-size: 150%; font-face: italics; }
  main h3 { font-size: 125%; }
  main h4 { font-size: 110%; }
  .emoji-key li { margin-bottom: 0.5em; }
  section::before { content: '' !important; }
  th { background-color: #555; color: white; }
  table.dataTable, .dataTables_scrollBody { margin: 0.5em 0; }
  #info { position: absolute; top: 2.5em; right: 2.5em; color: white; }
  #info a { color: white !important; }
  .quarto-dark tr.even { background-color: #333; }
  .quarto-dark tr.odd { background-color: #222; }
  .quarto-dark div.datatables { color: white; }
  .quarto-dark table.dataTable { border: 1px solid #555; }
  table strong { color: red; }
  .quarto-dark table strong { color: yellow; }
  summary { color: #333; }
  .quarto-dark summary { color: #CCC; }
  .validation { display: block; 
                border: 2px solid #15342A; 
                border-radius: 1em; 
                padding: 0.5em 1em 0; 
                margin-bottom: 0.5em;
                background-color: #15342A33;}
</style>

::: {#info}
[MetaCheck](http://www.scienceverse.org/metacheck) version {{< meta metacheck.version >}}  
Report Created: {{< meta metacheck.report-created >}}  
%s <!-- doi, if exists -->
:::

[Metacheck](https://www.scienceverse.org/metacheck/) is a tool that screens scientific manuscripts and aims to identify potential issues for improvement, thereby guiding researchers towards best practices. Metacheck is developed to help researchers correctly and completely report statistical results, automatically retrieve possible relevant information about citations, and improve how researchers share data, code, and preregistrations.

Metacheck combines existing and new checks in a module-based tool. It mainly relies on text search or retrieving information from external sources through API’s or web-scraping, but some modules also incorporate tools that use machine learning classifiers or large language models. The use of LLM's is always optional and opt-in. The development of Metacheck is guided by our [values statement](https://www.scienceverse.org/metacheck/#our-values). 


::: {.validation}
Our modules are validated on sets of open-access papers. In each validated module, there will be a sentence explaining the prevalence of false positives (incorrect detection/classification) and false negatives (incorrect omission). For example, if a hypothetical module detects the inappropriate practice of "woozling", the sentence might read:

> In a sample of 250 papers from the *Journal of X*, there were 350 instances of woozling. This module correctly detected 340 of them, and incorrectly identified 7. Therefore 3% of true instances are missed, and 2% of detections are false positives.

There is an inherent tradeoff between false positives and false negatives. Many of our modules are designed like "smoke detectors", where they are more likely to detect a practice that needs attention, but also more likely to incorrectly flag something. Therefore, you need to check the output of each module, keeping the validated error rates in mind.
:::

Metacheck is under continuous development. Issues can be submitted [on Github](https://github.com/scienceverse/metacheck/issues), and suggestions for improvement or feedback can be sent to [metacheck@scienceverse.org](mailto:metacheck@scienceverse.org).

<!-- Demo -->

<div style="color: red; margin-top: 3em;">Everything below here is for test purposes and removed when using this template to create a report.</div>

```{r}
#| include: false
library(metacheck)
```

## Summary

- ✅️ [No problems detected](#module-1){.green} Detected evidence of good practice or no evidence of poor practice.
- 🔍 [Something to check](#module-2){.yellow}: Detected something you should check.
- ⚠️ [Possible problems detected](#module-3){.red}: A possible poor practice detected.
- ℹ️ [Informational only](#module-4){.info}: Info that isn't necessarily good/questionable/poor practice.
- ⚪️ [Not applicable](#module-5){.na}: This check isn't relevant to this paper.
- ☠️ [Check failed](#module-6){.fail}: This is usually when something goes wrong and there is an uncaught error in the module.

## General Modules

### ✅ Module 1 {.green}

Detected evidence of good practice or no evidence of poor practice.

<details>
  <summary>View feedback</summary>
  <div>
Adipiscing massa leo neque cubilia, volutpat, curae aptent scelerisque, eget quam placerat. Vitae inceptos himenaeos gravida semper viverra platea. Lacus ac congue facilisis urna pharetra ornare fermentum commodo, senectus fames dictumst magna tempor.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(id = 1:3, text = c("Dolor urna mus libero dui consequat quisque sapien nibh curae eros.", 
"Consectetur hac integer urna pharetra ridiculus penatibus magna magnis nisi ac?", 
"Adipiscing ultrices imperdiet lectus bibendum massa facilisis suscipit."
)), class = "data.frame", row.names = c(NA, -3L))

# display table -----------------------------------
metacheck::report_table(table, c(.1, .9), 3, FALSE)
```

```{r}
#| results: 'asis'

marg_ref <- bibentry(
  bibtype = "Article",
  title = "The Prevalence of Marginally Significant Results in Psychology Over Time",
  author = "Olsson-Collentine, A., van Assen, M. A. L. M., & Hartgerink, C. H. J.",
  year = "2019",
  journal = "Psychological Science",
  volume = 30,
  issue = 4,
  pages = "576--586",
  doi = "10.1177/0956797619830326"
)

format_ref(marg_ref) |> cat()
```

`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

::: {.callout-note title="How It Works" collapse="true"}

Demo description

Demo details...

This module was developed by Lisa DeBruine and Daniel Lakens

:::

<p class="validation">In a sample of 250 papers from *Psychological Science*, there were 350 instances of woozling. This module correctly detected 340 of them, and incorrectly identified 7. Therefore 3% of true instances are missed, and 2% of detections are false positives.</p>

### 🔍 Module 2 {#module-2 .yellow}

Detected something you should check.

<details>
  <summary>View feedback</summary>
  <div>

Elit potenti aliquet, pulvinar est nascetur felis cubilia vel scelerisque dapibus mus conubia. Ut laoreet taciti morbi cum.

```{r}
#| echo: false

# table data ------------------------------------
table <- structure(list(c(
  "Amet accumsan inceptos aliquam cras non commodo sapien vulputate diam odio fermentum magnis ornare tristique.", 
  "Lorem habitant sem enim libero nostra lacus pharetra aptent rutrum vehicula.",
  "Ipsum taciti non pharetra morbi bibendum sociis congue risus pellentesque elementum!", 
  "Elit fringilla penatibus proin diam erat torquent iaculis vestibulum platea dictumst ligula.", 
  "Amet conubia ultricies arcu consequat mattis auctor metus."
)), names = "", class = "data.frame", row.names = c(NA, -2L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

::: {.callout-note title="How It Works" collapse="true"}

Demo description

Demo details...

This module was developed by Lisa DeBruine and Daniel Lakens

:::

<p class="validation">In a sample of 100 papers from *PLoS One*, there were 10 papers with stapling. This module correctly detected 10 of them, and incorrectly identified 5. Therefore 0% of true instances are missed, and 33% of detections are false positives.</p>

### ⚠️ Module 3 {#module-3 .red}

A possible poor practice detected.

<details>
  <summary>View feedback</summary>
  <div>
  
Ipsum in magnis proin ligula nisi parturient, morbi sagittis dis tellus. Pretium ante mauris nulla ac, fusce sollicitudin feugiat semper fermentum massa? Ullamcorper a tellus, pulvinar augue montes molestie proin quis molestie tortor. Habitant conubia cursus conubia, odio duis, pharetra, ad magnis pretium. Sem montes nullam vitae faucibus nunc pulvinar ultrices dignissim risus imperdiet eros fames viverra semper.

Elit porta mattis, inceptos euismod massa enim aenean ullamcorper netus odio nunc. Molestie arcu montes at nisl eget sed.

Ipsum viverra quam nunc ullamcorper congue aptent molestie vivamus per quam cursus parturient? Quam montes euismod pellentesque magnis torquent magna, iaculis mollis suspendisse? Semper ut primis auctor a tempus duis libero sociosqu fringilla. Phasellus neque vitae fusce tincidunt velit sapien – sodales eleifend orci nisl. Blandit platea nullam quisque, donec tempor curabitur posuere cursus? Platea vivamus malesuada, risus habitant ultrices conubia semper dui proin nibh.

```{r}
#| echo: false
# table data ------------------------------------
table <- structure(list(id = 1:5, text = c("Lorem semper tempus libero habitant faucibus cursus venenatis natoque volutpat est ultricies penatibus nisl lacinia.", 
"Lorem cras bibendum facilisi porta sagittis a convallis fames erat dui netus cubilia.", 
"Adipiscing auctor litora scelerisque tincidunt ullamcorper volutpat mattis ultrices lectus rutrum.", 
"Elit nisi cras pharetra etiam semper sollicitudin interdum magnis facilisi.", 
"Ipsum per platea varius vel condimentum posuere gravida cum laoreet commodo."
)), class = "data.frame", row.names = c(NA, -5L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

::: {.callout-note title="How It Works" collapse="true"}

Demo description

Demo details...

This module was developed by Lisa DeBruine and Daniel Lakens

:::

<p class="validation">In a sample of 100 papers from *PLoS One*, there were 10 instances of noodling. This module correctly detected 9 of them, and incorrectly identified 9. Therefore 10% of true instances are missed, and 50% of detections are false positives.</p>

## Introduction Modules

### ℹ️ Module 4 {#module-4 .info}

Summary text...

<details>
  <summary>View feedback</summary>
  <div>
    
`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

::: {.callout-note title="How It Works" collapse="true"}

Demo description

Demo details...

This module was developed by Lisa DeBruine and Daniel Lakens

:::

<p class="validation">Validation text...</p>

## Methods Modules

### ⚪️ Module 5 {#module-5 .na}

This check isn't relevant to this paper.

<details>
  <summary>View feedback</summary>
  <div>
    
`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

::: {.callout-note title="How It Works" collapse="true"}

Demo description

Demo details...

This module was developed by Lisa DeBruine and Daniel Lakens

:::

<p class="validation">Validation text...</p>

## Results Modules

### ☠️ Module 6 {#module-6 .fail}

This is usually when something goes wrong and there is an uncaught error in the module.

<details>
  <summary>View feedback</summary>
  <div>
  
`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

::: {.callout-note title="How It Works" collapse="true"}

Demo description

Demo details...

This module was developed by Lisa DeBruine and Daniel Lakens

:::

<p class="validation">Validation text...</p>

## Discussion Modules

### ℹ️ Module 7 Has a Long Name {#module-7 .info}

Summary text...

<details>
  <summary>View feedback</summary>
  <div>
  
`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

::: {.callout-note title="How It Works" collapse="true"}

Demo description

Demo details...

This module was developed by Lisa DeBruine and Daniel Lakens

:::

<p class="validation">Validation text...</p>

## References Modules

### ℹ️ Module 8 Has an Even Longer Name {#module-8 .info}

Summary text...

<details>
  <summary>View feedback</summary>
  <div>
  
`r collapse_section("Ipsum porta diam cursus quam viverra consequat?")`

  </div>
</details>

::: {.callout-note title="How It Works" collapse="true"}

Demo description

Demo details...

This module was developed by Lisa DeBruine and Daniel Lakens

:::

<p class="validation">Validation text...</p>
