---
title: MetaCheck Report
subtitle: "To Err is Human: An Empirical Investigation"
metacheck:
  version: "0.0.1.9003"
  report-created: "2026-04-17"
format:
  html:
    theme: 
      light: flatly
      dark: darkly
    respect-user-color-scheme: true
    toc: true
    toc-title: >
      <ul class="emoji-key">
        <li class="red">⚠️ possible problems detected;</li> 
        <li class="yellow">🔍 something to check;</li> 
        <li class="green">✅️ no problems detected;</li>  
        <li class="info">ℹ️ informational only;</li>  
        <li class="na">⚪️ not applicable;</li>  
        <li class="fail">☠️ check failed</li>
      <ul>
      <hr/>
      **Table of Contents**
    toc-location: right
    toc-expand: 3
    page-layout: full
    title-block-banner: "#15342A"    #"#327118"
    title-block-banner-color: "white"
    link-external-newwindow: true
    embed-resources: true
    format-links: false
    smooth-scroll: true
execute: 
  echo: false
  error: true
---

<style>
  #TOC * { border-left: none; }
  #TOC > ul { border-left: 1px solid #15342A; }
  #TOC > ul > li > ul > li { text-indent: -1.2em; margin-left: 1.2em; }
  main h2, main h3 { margin-left: -20px; }
  main h2 { font-size: 150%; font-face: italics; }
  main h3 { font-size: 125%; }
  main h4 { font-size: 110%; }
  .emoji-key li { margin-bottom: 0.5em; }
  section::before { content: '' !important; }
  th { background-color: #555; color: white; }
  table.dataTable, .dataTables_scrollBody { margin: 0.5em 0; }
  #info { position: absolute; top: 2.5em; right: 2.5em; color: white; }
  #info a { color: white !important; }
  .quarto-dark tr.even { background-color: #333; }
  .quarto-dark tr.odd { background-color: #222; }
  .quarto-dark div.datatables { color: white; }
  .quarto-dark table.dataTable { border: 1px solid #555; }
  table strong { color: red; }
  .quarto-dark table strong { color: yellow; }
  summary { color: #333; }
  .quarto-dark summary { color: #CCC; }
</style>

::: {#info}
[MetaCheck](http://www.scienceverse.org/metacheck) version {{< meta metacheck.version >}}  
Report Created: {{< meta metacheck.report-created >}}  
NA <!-- doi, if exists -->
:::

[Metacheck](https://www.scienceverse.org/metacheck/) is a tool that screens scientific manuscripts and aims to identify potential issues for improvement, thereby guiding researchers towards best practices. Metacheck is developed to help researchers correctly and completely report statistical results, automatically retrieve possible relevant information about citations, and improve how researchers share data, code, and preregistrations.

::: {.callout-tip title="Learn More" collapse="true"}

Metacheck combines existing and new checks in a module-based tool. It mainly relies on text search, retrieving information from external sources through API’s or web-scraping, but it also incorporates tool that use machine learning classifiers or large language models. The use of LLM’s is always optional. The development of Metacheck is guided by our [values statement](https://docs.google.com/document/d/1bbIkgUaiz3fpTXAeTF3h-gsfhqWEBN_n6OBcbFLfXjw/edit?tab=t.0). 

Metacheck often needs to balance false positives against false negatives, and prioritizes preventing false negatives. Like a spelling checker, which often highlights words that are not spelled incorrectly, Metacheck modules will contain false positives. We hope their rate is acceptable, given opportunities for improvement that Metacheck identifies. Modules are currently primarily validated on the psychological literature.

Metacheck is under continuous development. Issues can be submitted [on Github](https://github.com/scienceverse/metacheck/issues), and suggestions for improvement or feedback can be sent to D.Lakens@tue.nl.

:::


## Summary

- ⚠️ [Funding Check](#funding-check){.red}: No funding statement was detected.  
- ✅️ [Open Practices Check](#open-practices-check){.green}: Shared data and code detected.  
- ✅️ [COI Check](#coi-check){.green}: A conflict of interest statement was detected.  
- ⚠️ [Power Analysis Check](#power-analysis-check){.red}: We detected 2 potential power analyses.  
- ⚠️ [Exact P-Values](#exact-p-values){.red}: We found 1 imprecise *p* value out of 3 detected.  
- ⚠️ [Marginal Significance](#marginal-significance){.red}: You described 2 effects with terms related to 'marginally significant'.  
- ⚠️ [StatCheck](#statcheck){.red}: 1 possible error in t-tests or F-tests  
- 🔍 [Non-Significant P Value Check](#non-significant-p-value-check){.yellow}: We found 2 non-significant p values that should be checked for appropriate interpretation.  
- 🔍 [Effect Sizes in t-tests and F-tests](#effect-sizes-in-t-tests-and-f-tests){.yellow}: We found 1 t-test and/or F-test where effect sizes are not reported.  
- 🔍 [Repository Check](#repository-check){.yellow}: 
    -  We found 9 files in 3 repositories.
    -  We found 1 README file and 2 repositories without READMEs.
    -  We found 1 archive file.  
- 🔍 [Code Check](#code-check){.yellow}: 
    -  We found 4 R, SAS, SPSS, or Stata code files.
    -  1 code file had no comments.
    -  1 file loaded in the code was missing in the repository.
    -  Absolute file paths were found.
    -  Libraries/imports were loaded in multiple places.  
- 🔍 [Reference Accuracy](#reference-accuracy){.yellow}: We checked 5 references in CrossRef and found entries for 4.  
- ℹ️ [Replication Check](#replication-check){.info}: We found 1 replication for 1 original you cited.  
- ℹ️ [RetractionWatch](#retractionwatch){.info}: You cited 1 article in the RetractionWatch database.  
- ℹ️ [Check PubPeer Comments](#check-pubpeer-comments){.info}: You cited 1 reference with comments in PubPeer.  
- ℹ️ [Summarise References](#summarise-references){.info}: Summary information provided for 5 references  
- ☠️ [causal_claims](#causal_claims){.fail}: This module failed to run  



## General Modules

### ⚠️ Funding Check {#funding-check .red}

No funding statement was detected. Consider adding one.

::: {.callout-note title="How It Works" collapse="true"}

Identify and extract funding statements.

The Funding Check module uses regular expressions to check sentences for words related to funding statements. It will return the sentences in which the conflict of interest statement was found.

The function incorporates code from [rtransparent](https://github.com/serghiou/rtransparent), which is no longer maintained. For their validation, see [the paper](https://doi.org/10.1371/journal.pbio.3001107).

This module was developed by Daniel Lakens

:::

### ✅️ Open Practices Check {#open-practices-check .green}

Shared data and code detected.

<details><summary>View detailed feedback</summary><div>

Data was openly shared for this article, based on the following text:

> Data is also available from https://osf.io/5tbm9 and code is also available from https://osf.io/629bx.

Code was openly shared for this article, based on the following text:

> Data and analysis code is available on GitHub from https://github.com/Lakens/to_err_is_human and from https://researchbox.org/4377.

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module incorporates ODDPub into metacheck. ODDPub is a text mining algorithm that detects which publications disseminated Open Data or Open Code together with the publication.

The Open Practices Check runs Open Data Detection in Publications (ODDPub). ODDPub searches for text expressions that indicate that an article shared Open Data or Open Code together with the publication. More information on the package can be found at <https://github.com/quest-bih/oddpub>. The module only returns whether open data and code is found (the original package offers more fine-grained results). The tool was validated in the biomedical literature, see <https://osf.io/yv5rx/>.

ODDPub was developed by Nico Riedel, Vladislav Nachev, Miriam Kip, and Evgeny Bobrov at the QUEST Center for Transforming Biomedical Research, Berlin Institute of Health. <https://doi.org/10.5334/dsj-2020-042>

It might miss open data and code declarations when the words used in the manuscript are not in the pattern that ODDPub searches for, or when the repositories are not in the ODDpub code (e.g., ResearchBox).

From ODDPub: "To validate the algorithm, we manually screened a sample of 792 publications that were randomly selected from PubMed. On this validation dataset, our algorithm detects Open Data publications with a sensitivity of 0.73 and specificity of 0.97."

This module was developed by Daniel Lakens

:::

### ✅️ COI Check {#coi-check .green}

A conflict of interest statement was detected.

<details><summary>View detailed feedback</summary><div>

The following conflict of interest statement was detected.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("The authors declare a conflict of interest."), names = "", class = "data.frame", row.names = c(NA, 
-1L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Identify and extract Conflicts of Interest (COI) statements.

The COI Check module uses regular expressions to check sentences for words related to conflict of interest statements. It will return the sentences in which the conflict of interest statement was found.

The function incorporates code from [rtransparent](https://github.com/serghiou/rtransparent), which is no longer maintained. For their validation, see [the paper](https://doi.org/10.1371/journal.pbio.3001107).

This module was developed by Daniel Lakens

:::

## Method Modules

### ⚠️ Power Analysis Check {#power-analysis-check .red}

We detected 2 potential power analyses.

<details><summary>View detailed feedback</summary><div>

Some essential information could not be detected: alpha_level, effect_size, effect_size_metric

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(power_id = 1:2, power_type = c("sensitivity", 
"apriori"), statistical_test = c("other", "t-test"), sample_size = c(50L, 
50L), alpha_level = c(NA, 0.05), power = c(0.8, 0.8), effect_size = c(0.5, 
NA), effect_size_metric = c("Cohen's d", NA), software = c("other", 
"R (pwr package)")), row.names = c(NA, -2L), class = c("tbl_df", 
"tbl", "data.frame"))

# display table -----------------------------------
metacheck::report_table(table, "auto", 5, FALSE)
```

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(power_id = c("1", "2"), text = c("We conducted a <strong>sensitivity</strong> <strong>power</strong> analysis 2 to determine that a Cohen's d of 0.50 is the smallest effect size that we could detect with N=50 participants in each group and 80% <strong>power</strong>.", 
"pwr::pwr.t.test(n = 50, <strong>power</strong> = 0.8, alternative = \"greater\")"
)), row.names = c(NA, -2L), class = c("tbl_df", "tbl", "data.frame"
))

# display table -----------------------------------
metacheck::report_table(table, "auto", 1, FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

Power analyses need to contain the following information to be interpretable: the type of power analysis, the statistical test, the software used, sample size, critical alpha criterion, power level, effect size, and an effect size metric. In addition, it is recommended to make sure the power analysis is reproducible (by sharing the code, or a screenshot, of the power analysis), and to provide good arguments for why the study was designed to detect an effect of this size.

For an a-priori power analysis, where the sample size is determined, reporting all information would look like:

> An a priori power analysis for an independent samples t-test, conducted using the pwr.t.test function from pwr (Champely, 2020), indicated that for a Cohen's d = 0.5, an alpha level of 0.05, and a desired power level of 80% required at least 64 participants in each group.

For a sensitivity power analysis, this sentence would look like:

> A sensitivity power analysis for an independent samples t-test, conducted using the pwr.t.test function from pwr (Champely, 2020), indicated that with 64 participants in each group, and an alpha level of 0.05, a desired power level of 80% was reached for an effect size of d = 0.5.

:::

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module uses uses regular expressions to identify sentences that contain a statistical power analysis. If specified by the user, it also uses a large language module (LLM) to extract information reported in power analyses, including the statistical test, sample size, alpha level, desired level of power, and magnitude and type of effect size.

The Power Analysis Check module uses regular expressions to identify sentences that contain a statistical power analysis. Without the use of an LMM, the module uses regular expressions to classify the power analysis as a-priori, sensitivity or post-hoc. With the use of an LMM, it checks if the power analysis is reported with all required information.

The regular expressions can miss power analyses, or fail to classify them correctly. The type of power analysis is often difficult to classify, which can easily be solved by explicitly specifying the type of power analysis as 'a-priori', 'sensitivity', or 'post-hoc'. Note that 'post-hoc' or 'observed' power is rarely useful. The LMM can fail to identify information in the paper, and will not have access to information in paragraphs in the paper other than those that contain the word 'power'. This package was validated by the Metacheck team on articles in Psychological Science.

This module was developed by Lisa DeBruine, Daniel Lakens and Cristian Mesquida

:::

## Results Modules

### ⚠️ Exact P-Values {#exact-p-values .red}

We found 1 imprecise *p* value out of 3 detected.

<details><summary>View detailed feedback</summary><div>

Reporting *p* values imprecisely (e.g., *p* < .05) reduces transparency, reproducibility, and re-use (e.g., in *p* value meta-analyses). Best practice is to report exact p-values with three decimal places (e.g., *p* = .032) unless *p* values are smaller than 0.001, in which case you can use *p* < .001.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("P-Value" = "p > .05", Text = "There was no effect of experience on the reduction in errors when using the tool (p > .05), as the correlation was non-significant (Figure 2)."), row.names = c(NA, 
-1L), class = c("tbl_df", "tbl", "data.frame"))

# display table -----------------------------------
metacheck::report_table(table, c(0.1, 0.9), 2, FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

The APA manual states: Report exact *p* values (e.g., *p* = .031) to two or three decimal places. However, report *p* values less than .001 as *p* < .001. However, 2 decimals is too imprecise for many use-cases (e.g., a *p* value meta-analysis), so report *p* values with three digits.

American Psychological Association (2020). <em>Publication manual of the American Psychological Association</em>, 7 edition. American Psychological Association.

:::

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

List any p-values reported with insufficient precision (e.g., p < .05 or p = n.s.)

This module uses regular expressions to identify p-values. It will flag any values reported as p > ? or p < numbers greater than .001.

We try to exclude figure and table notes like "* p < .05", but may not succeed at excluding all false positives.

This module was developed by Lisa DeBruine

:::

### ⚠️ Marginal Significance {#marginal-significance .red}

You described 2 effects with terms related to 'marginally significant'.

<details><summary>View detailed feedback</summary><div>

You described effects with terms related to 'marginally significant'. If *p* values above 0.05 are interpreted as an effect, you inflate the alpha level, and increase the Type 1 error rate. If a *p* value is higher than the prespecified alpha level, it should be interpreted as a non-significant result.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Text = c("The paper shows examples of (1) open and closed OSF links; (2a) citation of retracted papers, (2b) citations without a doi, (2c) citations with Pubpeer comments, (2d) citations in the FLoRA replication database, and (2e) missing/mismatched/incorrect citations and references; (3a) R files with code on GitHub that do not load libraries in one location, (3b) load files that are not shared in the repository, (3c) lack comments, and (3d) have absolute file paths; (4) imprecise reporting of non-significant p-values; (5) tests with and without effect sizes; (6) use of \"marginally significant\" to describe non-significant findings; (7) a power analysis reporting some of the essential attributes; and (8) retrieving information from preregistrations.", 
"On average researchers in the experimental condition found the app marginally significantly more useful (M=5.06) than researchers in the control condition found the checklist (M=4.5), t(97.2)=-1.96, p=0.152."
), "Section Header" = c("Abstract", "Results")), row.names = c(NA, 
-2L), class = c("tbl_df", "tbl", "data.frame"))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

For metascientific articles demonstrating the rate at which non-significant p-values are interpreted as marginally significant, see:

Olsson-Collentine, A., van Assen, M. MAL, Hartgerink &amp;, J. CH (2019). &ldquo;The Prevalence of Marginally Significant Results in Psychology Over Time.&rdquo; <em>Psychological Science</em>, <b>30</b>, 576&ndash;586. <a href="https://doi.org/10.1177/0956797619830326">doi:10.1177/0956797619830326</a>.

For the list of terms used to identifify marginally significant results, see this [blog post by Matthew Hankins](https://web.archive.org/web/20251001114321/https://mchankins.wordpress.com/2013/04/21/still-not-significant-2/).

:::

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

List all sentences that describe an effect as 'marginally significant'.

The marginal module searches for regular expressions that match a predefined pattern. The list of terms is a subset of those listed in a [blog post by Matthew Hankins](https://web.archive.org/web/20251001114321/https://mchankins.wordpress.com/2013/04/21/still-not-significant-2/). The module returns all sentences that match terms describing ‘marginally significant’ results.

Some of the terms identified might not be problematic in some contexts, and there are ways to describe ‘marginal significance’ that are not detected by the module.

This module was developed by Daniel Lakens

:::

### ⚠️ StatCheck {#statcheck .red}

1 possible error in t-tests or F-tests

<details><summary>View detailed feedback</summary><div>

We detected possible errors in test statistics. Note that as the accuracy of statcheck has only been validated for *t*-tests and *F*-tests. As Metacheck only uses validated modules, we only provide statcheck results for *t* tests and *F*-tests.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Text = "t(97.2)=-1.96, p=0.152", "Recomputed p" = 0.05286, 
    Sentence = "On average researchers in the experimental condition found the app marginally significantly more useful (M=5.06) than researchers in the control condition found the checklist (M=4.5), t(97.2)=-1.96, p=0.152."), row.names = 1L, class = c("statcheck", 
"data.frame"))

# display table -----------------------------------
metacheck::report_table(table, c("10em", NA, NA, NA), 2, FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

For metascientific research on the validity of statcheck, and it's usefulness to prevent statistical reporting errors, see:

Nuijten M, van Assen M, Hartgerink C, Epskamp S, Wicherts J (2017). &ldquo;The validity of the tool &quot;statcheck&quot; in discovering statistical reporting inconsistencies.&rdquo; <a href="https://doi.org/10.31234/osf.io/tcxaja">doi:10.31234/osf.io/tcxaja</a>, Preprint.

Nuijten M, Wicherts J (2023). &ldquo;The effectiveness of implementing statcheck in the peer review process to avoid statistical reporting errors.&rdquo; <a href="https://doi.org/10.31234/osf.io/bxau9">doi:10.31234/osf.io/bxau9</a>, Preprint.

:::

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Check consistency of p-values and test statistics

The Statcheck module runs Statcheck. Statcheck searches for regular expressions that match a predefined pattern, and identifies APA reported statistical tests. More information on the package can be found at <https://github.com/cran/statcheck>. The module only returns Statcheck results for t-tests and F-tests, as these are the only tests which have been validated, see <https://osf.io/preprints/psyarxiv/tcxaj_v1/>.

Statcheck was developed by Michèle Nuijten and Sascha Epskamp.

Statcheck considers p = 0.000 an error, as you should report p < 0.001. Furthermore, p < 0.03 is an error if the p-value was 0.031, and one should simply report exact p-values (p = 0.031). Statcheck might miss one-sided tests, and falsely assume the p-value is incorrect. For more information, see [StatCheck](https://statcheck.io/).

This module was developed by Daniel Lakens and Lisa DeBruine

:::

### 🔍 Non-Significant P Value Check {#non-significant-p-value-check .yellow}

We found 2 non-significant p values that should be checked for appropriate interpretation.

<details><summary>View detailed feedback</summary><div>

Meta-scientific research has shown nonsignificant p values are commonly misinterpreted. It is incorrect to infer that there is 'no effect', 'no difference', or that groups are 'the same' after p > 0.05.

It is possible that there is a true non-zero effect, but that the study did not detect it. Make sure your inference acknowledges that it is possible that there is a non-zero effect. It is correct to include the effect is 'not significantly' different, although this just restates that p > 0.05.

Metacheck does not yet analyze automatically whether sentences which include non-significant p-values are correct, but we recommend manually checking the sentences below for possible misinterpreted non-significant p values.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Text = c("p=0.152", "p > .05"), Sentence = c("On average researchers in the experimental condition found the app marginally significantly more useful (M=5.06) than researchers in the control condition found the checklist (M=4.5), t(97.2)=-1.96, p=0.152.", 
"There was no effect of experience on the reduction in errors when using the tool (p > .05), as the correlation was non-significant (Figure 2)."
)), row.names = c(NA, -2L), class = c("tbl_df", "tbl", "data.frame"
))

# display table -----------------------------------
metacheck::report_table(table, c(0.1, 0.9), 2, FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

For metascientific articles demonstrating the rate of misinterpretations of non-significant results is high, see:

Aczel B, Palfi B, Szollosi A, Kovacs M, Szaszi B, Szecsi P, Zrubka M, Gronau Q, van den Bergh D, Wagenmakers E (2018). &ldquo;Quantifying Support for the Null Hypothesis in Psychology: An Empirical Investigation.&rdquo; <em>Advances in Methods and Practices in Psychological Science</em>, <b>1</b>(3), 357&ndash;366. <a href="https://doi.org/10.1177/2515245918773742">doi:10.1177/2515245918773742</a>.

Murphy S, Merz R, Reimann L, Fernández A (2025). &ldquo;Nonsignificance misinterpreted as an effect’s absence in psychology: Prevalence and temporal analyses.&rdquo; <em>Royal Society Open Science</em>, <b>12</b>(3), 242167. <a href="https://doi.org/10.1098/rsos.242167">doi:10.1098/rsos.242167</a>.

For educational material on preventing the misinterpretation of p values, see [Improving Your Statistical Inferences](https://lakens.github.io/statistical_inferences/01-pvalue.html#sec-misconception1).

:::

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module checks for imprecisely reported p values. If p > .05 is detected, it warns for misinterpretations.

The nonsignificant p-value check searches for regular expressions that match a predefined pattern. The module identifies all p-values in a manuscript and selects those that are not reported to be smaller than or equal to 0.05. It returns all sentences containing non-significant p-values.

In the future, the Metacheck team aims to incorporate a machine learning classifier to only return sentences likely to contain misinterpretations. If you want to help to improve the module, reach out to the Metacheck development team.

This module was developed by Daniel Lakens

:::

### 🔍 Effect Sizes in t-tests and F-tests {#effect-sizes-in-t-tests-and-f-tests .yellow}

We found 1 t-test and/or F-test where effect sizes are not reported.

<details><summary>View detailed feedback</summary><div>

We recommend checking the sentences below, and add any missing effect sizes.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("On average researchers in the experimental condition found the app marginally significantly more useful (M=5.06) than researchers in the control condition found the checklist (M=4.5), t(97.2)=-1.96, p=0.152."), names = "", class = "data.frame", row.names = c(NA, 
-1L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

For metascientific articles demonstrating that effect sizes are often not reported:

* Peng, C.-Y. J., Chen, L.-T., Chiang, H.-M., & Chiang, Y.-C. (2013). The Impact of APA and AERA Guidelines on Effect Size Reporting. Educational Psychology Review, 25(2), 157–209. doi:[10.1007/s10648-013-9218-2](https://doi.org/10.1007/s10648-013-9218-2).

For educational material on reporting effect sizes:

* [Guide to Effect Sizes and Confidence Intervals](https://matthewbjane.quarto.pub/guide-to-effect-sizes-and-confidence-intervals/)

:::

::: {.callout-tip title="All detected and assessed stats" collapse="true"}

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Sentence = c("On average researchers in the experimental (app) condition made fewer mistakes (M=9.12) than researchers in the control (checklist) condition (M=10.9) t(97.7)=2.9 p=0.005 d=0.59.", 
"On average researchers in the experimental condition found the app marginally significantly more useful (M=5.06) than researchers in the control condition found the checklist (M=4.5), t(97.2)=-1.96, p=0.152."
), "Effect Size" = c("d=0.59", NA), "Reported Test" = c("t(97.7)=2.9", 
"t(97.2)=-1.96"), "Test Type" = c("t-test", "t-test")), row.names = c(NA, 
-2L), class = c("tbl_df", "tbl", "data.frame"))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

:::

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

The Effect Size module checks for effect sizes in t-tests and F-tests.

The Effect Size check searches for regular expressions that match a predefined pattern. The module was validated on APA reported statistical tests, and might miss effect sizes that were reported in other reporting styles. It was validated by the Metacheck team on papers published in Psychological Science.

If you want to extend the package to detect effect sizes for additional tests, reach out to the Metacheck development team.

This module was developed by Daniel Lakens and Lisa DeBruine

:::

### 🔍 Repository Check {#repository-check .yellow}

-  We found 9 files in 3 repositories.
-  We found 1 README file and 2 repositories without READMEs.
-  We found 1 archive file.

<details><summary>View detailed feedback</summary><div>

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Repository = c("<a href='osf.io/629bx' target='_blank'>osf.io/629bx</a>", 
"<a href='https://github.com/Lakens/to_err_is_human' target='_blank'>github.com/Lakens/to_err_is_human</a>", 
"<a href='osf.io/48ncu ' target='_blank'>osf.io/48ncu </a>"), 
    Platform = c("osf", "github", NA), "All Files" = c(4L, 2L, 
    3L), "Data Files" = c(1L, 1L, 0L), "Code Files" = c(2L, 1L, 
    1L), READMEs = c(0L, 0L, 1L), Archives = c(1L, 0L, 0L)), row.names = c(NA, 
-3L), class = c("tbl_df", "tbl", "data.frame"))

# display table -----------------------------------
metacheck::report_table(table, "auto", 10, FALSE)
```

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Repository = c("osf.io/48ncu ", "osf.io/48ncu ", 
"osf.io/48ncu ", "osf.io/629bx", "osf.io/629bx", "osf.io/629bx", 
"osf.io/629bx", "https://github.com/Lakens/to_err_is_human", 
"https://github.com/Lakens/to_err_is_human"), File = c("<a href='https://osf.io/download/jz6v5/' target='_blank'>README</a>", 
"<a href='https://osf.io/download/6929f4994ce565d35f957294/' target='_blank'>papercheck.png</a>", 
"<a href='https://osf.io/download/2y3g5/' target='_blank'>test_script.R</a>", 
"<a href='https://osf.io/download/6935bc117049c887a125cb25/' target='_blank'>bad.R</a>", 
"<a href='https://osf.io/download/uq347/' target='_blank'>bad.Rmd</a>", 
"<a href='https://osf.io/download/6935c4679ca0f02ea72a1a31/' target='_blank'>example2.csv</a>", 
"<a href='https://osf.io/download/6976438ff9da155d0565c720/' target='_blank'>Archive.zip</a>", 
"<a href='https://raw.githubusercontent.com/Lakens/to_err_is_human/main/analysis.R' target='_blank'>analysis.R</a>", 
"<a href='https://raw.githubusercontent.com/Lakens/to_err_is_human/main/file2.csv' target='_blank'>file2.csv</a>"
), Size = c("30 B", "1.6 MB", "183 B", "172 B", "413 B", "5 B", 
"6.4 kB", "306 B", "794 B"), Type = c("readme", "image", "code", 
"code", "code", "data", "archive", "code", "data")), row.names = c(NA, 
9L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, "auto", 10, FALSE)
```

README files are a way to document the contents and structure of a folder, helping users locate the information they need. You can use a README to document changes to a repository, and explain how files are named. Please consider adding a README to each repository.

The following files are archives: Archive.zip. We did not examine their content. Consider uploading these individually to improve discoverability and re-use.

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module retrieves information from repositories.

The Repository Check module lists files on the OSF, GitHub, and ResearchBox based on links in the manuscript.

If you want to extend the package to be able to download files from additional data repositories reach out to the Metacheck development team.

This module was developed by Daniel Lakens and Lisa DeBruine

:::

### 🔍 Code Check {#code-check .yellow}

-  We found 4 R, SAS, SPSS, or Stata code files.
-  1 code file had no comments.
-  1 file loaded in the code was missing in the repository.
-  Absolute file paths were found.
-  Libraries/imports were loaded in multiple places.

<details><summary>View detailed feedback</summary><div>

Below, we describe some best coding practices and give the results of automatic evaluation of these practices in the code files below. This check may miss things or produce false positives if your scripts are less typical.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("File Name" = c("<a href='https://osf.io/download/2y3g5/' target='_blank'>test_script.R</a>", 
"<a href='https://osf.io/download/6935bc117049c887a125cb25/' target='_blank'>bad.R</a>", 
"<a href='https://osf.io/download/uq347/' target='_blank'>bad.Rmd</a>", 
"<a href='https://raw.githubusercontent.com/Lakens/to_err_is_human/main/analysis.R' target='_blank'>analysis.R</a>"
), "% Comments" = c("17%", "7%", "26%", "0%"), "Missing Files" = c(1L, 
0L, 0L, 0L), "Absolute Paths" = c(1L, 1L, 2L, 1L), "Code Between Libraries" = c(NA, 
12L, 13L, 10L)), row.names = c(NA, 4L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, "auto", 5, FALSE)
```

#### Code Comments

Best programming practice is to add comments to code, to explain what the code does (to yourself in the future, or peers who want to re-use your code).

#### Missing Files

The scripts load files, but 1 script loaded 1 file that could not be automatically identified in the repository. Check if the following files are made available, so that others can reproduce your code, or that the files are missing:

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("File name" = "test_script.R", "Missing Files" = "file.csv"), row.names = 1L, class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, "auto", 5, FALSE)
```

#### Absolute Paths

Best programming practice is to use relative file paths instead of absolute file paths (e.g., C://Lakens/files) as these folder names do not exist on other computers. The following absolute file paths were found in 4 code files:

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("File name" = c("test_script.R", "bad.R", "bad.Rmd", 
"analysis.R"), "Absolute paths found" = c("abs_path_pc <- read.csv(\"C:/lisa/file.csv\")", 
"data <- read_csv(\"C://Lakens/files/example.csv\")", "data <- read_csv(\"C://Lakens/files/example.csv\"), data2 <- read_csv(\"C://Lakens/files/example2.csv\")", 
"data_1 <- read.csv(\"C:/path/to/a/file.csv\")")), row.names = c(NA, 
4L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, "auto", 5, FALSE)
```

#### Libraries / Imports

Best programming practice is to load all required libraries/imports in one block near the top of the code. In 3 code files, libraries/imports were at multiple places (i.e., with more than 3 non-comment lines in between).

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module retrieves information from repositories checked by repo_check about code files (R, SAS, SPSS, Stata).

The Code Check module checks R, Rmd, Qmd, SAS, SPSS, and Stata files, using regular expressions to check the code. The regular expression search will detect the number of comments, the lines at which libraries/imports are loaded, attempts to detect absolute paths to files, and lists files that are loaded, and checks if these files are in the repository. The module will return suggestions to improve the code if there are no comments, if libraries/imports are loaded in lines further than 4 lines apart, if files that are loaded are not in the repository, and if absolute file paths are found.

The regular expressions can miss information in code files, or falsely detect parts of the code as a fixed file path. Libraries/imports might be loaded in one block, even if there are more than 3 intermittent lines. The package was validated internally on papers published in Psychological Science. There might be valid reasons why some loaded files can’t be shared, but the module can’t evaluate these reasons, and always gives a warning.

If you want to extend the package to perform additional checks on code files, or make the checks work on other types of code files, reach out to the Metacheck development team.

This module was developed by Daniel Lakens

:::

## Reference Modules

### 🔍 Reference Accuracy {#reference-accuracy .yellow}

We checked 5 references in CrossRef and found entries for 4.

<details><summary>View detailed feedback</summary><div>

Double check any references listed in the tables below. This tool has a high false positive rate.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("References with Mismatched DOIs" = c("DeBruine, Lisa. 2025. Faux: Simulation for Factorial Designs. Zenodo. https://doi.org/10.5281/zenodo.2669586.", 
"Lakens, Daniël. 2018. \"Equivalence Testing for Psychological Research.\" Advances in Methods and Practices in Psychological Science 1: 259-70."
), "Original DOI" = c("10.5281/zenodo.2669586", ""), "CrossRef DOI" = c("10.32614/cran.package.faux", 
"10.1177/2515245918770963")), row.names = c(1L, 4L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, c(0.5, 0.25, 0.25), 5, FALSE)
```

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("References with Mismatched Years" = "DeBruine, Lisa. 2025. Faux: Simulation for Factorial Designs. Zenodo. https://doi.org/10.5281/zenodo.2669586.", 
    "Original Year" = 2025L, "CrossRef Year" = 2020L), row.names = 1L, class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, c(0.5, 0.25, 0.25), 5, FALSE)
```

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("References with Mismatched Titles" = "Gino, Francesca, and Scott S. Wiltermuth. 2014. \"Evil Genius? How Dishonesty Can Lead to Greater Creativity.\" Psychological Science 25 (4): 973–81. https://doi.org/10.1177/0956797614520714.", 
    "Original Title" = "Evil Genius? How Dishonesty Can Lead to Greater Creativity", 
    "CrossRef Title" = "Retracted: Evil Genius? How Dishonesty Can Lead to Greater Creativity"), row.names = 3L, class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, c(0.5, 0.25, 0.25), 5, FALSE)
```

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("References with Mismatched Authors" = "Lakens, Daniël. 2018. \"Equivalence Testing for Psychological Research.\" Advances in Methods and Practices in Psychological Science 1: 259-70.", 
    "Original Authors" = "Lakens, Daniël", "CrossRef Authors" = "Lakens, Daniel; Scheel, Anne M.; Isager, Peder Mortvedt"), row.names = 4L, class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, c(0.5, 0.25, 0.25), 5, FALSE)
```

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("References without Matches" = "Smith, F. 2021. \"Human Error Is a Symptom of a Poor Design.\" Journal of Journals. https://doi.org/10.0000/0123456789."), row.names = 5L, class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, 5, 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module checks references for mismatches with CrossRef.

This module uses the bib_match table from each paper (this can be added or refreshed using `add_bib_match()`) to detect possible problems in the reference section.

We check that the title from your reference section is the same as the retrieved title (ignoring differences in capitalisation) and that all author last names in your reference section are also in the retrieved author list (we do not check first names or order yet). This check is done for all references with crossref entries in the bib_match table.

Mismatches may be because of problems with our parsing of references from your PDF (we're working on improving this), incorrect formatting in CrossRef, or minor differences in punctuation.

This module was developed by Daniel Lakens and Lisa DeBruine

:::

### ℹ️ Replication Check {#replication-check .info}

We found 1 replication for 1 original you cited.

<details><summary>View detailed feedback</summary><div>

We checked 5 references with DOIs. We found 1 replication for 1 original you cited.

Check if you are aware of the replication studies, and cite them where appropriate.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Reference = "Eagly, Alice H., and Wendy Wood. 1999. \"The Origins of Sex Differences in Human Behavior: Evolved Dispositions Versus Social Roles.\" American Psychologist 54 (6): 408-23. https://doi.org/10.1037/0003-066x.54.6.408.", 
    Replication = "Zhang, L., Lee, A. J., DeBruine, L. M., & Jones, B. C. (2019). Are Sex Differences in Preferences for Physical Attractiveness and Good Earning Capacity in Potential Mates Smaller in Countries With Greater Gender Equality? Evolutionary Psychology, 17(2). <a href='https://doi.org/10.1177/1474704919852921' target='_blank'>doi:10.1177/1474704919852921</a>"), row.names = 1L, class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, c(0.5, 0.5), 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module checks references and warns for citations of original studies for which replication or reproduction studies exist in the FLoRA database.

The Replication Check module compares the reference list against studies in the FLoRA (FORRT Library of Replication Attempts) database based on the DOI. If a study in the database is found, a reminder is provided that a replication or reproduction of the original study exists, and should be cited (currently, a warning is provided regardless of whether the replication/reproduction study is already cited).

The module requires that the reference has a DOI. If you run the ref_doi_check module in a pipeline before this, it will use the enhanced DOI list from that module, otherwise it will only run on references with existing DOIs.

It is possible the original study was cited for other reasons than the empirical claim tested, or that the replication/reproduction in the FLoRA database is for only one of the studies in the paper, and not the study the authors discuss.

The database can be manually updated with the `FLoRA_update()` function. For more information, see <https://forrt.org/FLoRA/>.

This module was developed by Daniel Lakens, Lisa DeBruine and Lukas Wallrich

:::

### ℹ️ RetractionWatch {#retractionwatch .info}

You cited 1 article in the RetractionWatch database.

<details><summary>View detailed feedback</summary><div>

We checked 5 references with DOIs. You cited 1 article in the RetractionWatch database.

Check if you are aware of the replication studies, and cite them where appropriate.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Reference = "Gino, Francesca, and Scott S. Wiltermuth. 2014. \"Evil Genius? How Dishonesty Can Lead to Greater Creativity.\" Psychological Science 25 (4): 973–81. https://doi.org/10.1177/0956797614520714.", 
    "RW Type" = "Retraction"), class = "data.frame", row.names = c(NA, 
-1L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module checks references and warns for citations in the RetractionWatch Database.

The RetractionWatch Check module compares the reference list against studies in the RetractionWatch database based on the DOI. If a study in the database is found, a reminder is provided that the study was retracted, has an expression of concern, or a correction.

The module requires that the reference has a DOI. If you run the ref_doi_check module in a pipeline before this, it will use the enhanced DOI list from that module, otherwise it will only run on references with existing DOIs.

It is possible the authors are already aware that a study was retracted, but the module can't evaluate this.

The database can be manually updated with the rw_update function. For more information, see https://gitlab.com/crossref/retraction-watch-data.

This module was developed by Daniel Lakens and Lisa DeBruine

:::

### ℹ️ Check PubPeer Comments {#check-pubpeer-comments .info}

You cited 1 reference with comments in PubPeer.

<details><summary>View detailed feedback</summary><div>

We checked 5 references with DOIs. You cited 1 reference with comments in PubPeer.

Pubpeer is a platform for post-publication peer review. We have filtered out Pubpeer comments by 'Statcheck'. You can check out the comments by visiting the URLs below:

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Reference = "Gino, Francesca, and Scott S. Wiltermuth. 2014. \"Evil Genius? How Dishonesty Can Lead to Greater Creativity.\" Psychological Science 25 (4): 973–81. https://doi.org/10.1177/0956797614520714.", 
    Comments = 3, "PubPeer Link" = "<a href='https://pubpeer.com/publications/3FA648ECECB88454C91804F09E2E56' target='_blank'>link</a>"), row.names = 1L, class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module checks references and warns for citations that have comments on pubpeer (excluding Statcheck comments).

The PubPeer module uses the PubPeer API to check for each reference that has a DOI whether there are comments on the post-publication peer review platform. If comments are found, a link to the comments is provided. Comments by ‘Statcheck’ on PubPeer are ignored, see https://retractionwatch.com/2016/09/02/heres-why-more-than-50000-psychology-studies-are-about-to-have-pubpeer-entries/.

The module requires that the reference has a DOI. If you run the doi_check module in a pipeline before this, it will use the enhanced DOI list from that module, otherwise it will only run on references with existing DOIs.

For more information, see [PubPeer](https://www.pubpeer.com/static/about).

This module was developed by Daniel Lakens and Lisa DeBruine

:::

### ℹ️ Summarise References {#summarise-references .info}

Summary information provided for 5 references

<details><summary>View detailed feedback</summary><div>

See the specific reports above for details.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(text = c("DeBruine, Lisa. 2025. Faux: Simulation for Factorial Designs. Zenodo. https://doi.org/10.5281/zenodo.2669586.", 
"Eagly, Alice H., and Wendy Wood. 1999. \"The Origins of Sex Differences in Human Behavior: Evolved Dispositions Versus Social Roles.\" American Psychologist 54 (6): 408-23. https://doi.org/10.1037/0003-066x.54.6.408.", 
"Gino, Francesca, and Scott S. Wiltermuth. 2014. \"Evil Genius? How Dishonesty Can Lead to Greater Creativity.\" Psychological Science 25 (4): 973–81. https://doi.org/10.1177/0956797614520714.", 
"Lakens, Daniël. 2018. \"Equivalence Testing for Psychological Research.\" Advances in Methods and Practices in Psychological Science 1: 259-70.", 
"Smith, F. 2021. \"Human Error Is a Symptom of a Poor Design.\" Journal of Journals. https://doi.org/10.0000/0123456789."
), accuracy_mismatch = c("doi, year", NA, "title", "doi, author", 
"no match"), pubpeer = c(NA, NA, "<a href='https://pubpeer.com/publications/3FA648ECECB88454C91804F09E2E56' target='_blank'>Link</a>", 
NA, NA), replication_type = c(NA, "replication", NA, NA, NA), 
    retractionwatch = c(NA, NA, "Retraction", NA, NA)), class = "data.frame", row.names = c(NA, 
-5L))

# display table -----------------------------------
metacheck::report_table(table, c(0.75, NA, NA, NA, NA), 10, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Summarise information about each reference in a paper.

This module summarises previously-run reference section modules: ref_accuracy, ref_pubpeer, ref_replication, and ref_retraction.

This module was developed by Lisa DeBruine

:::




